Client-Side Indexes for Fast Full-Text Searching

### 2014-12-09 paper/paper.tex
initial stuff for ranking

Queries to our full-text search engine can be words or phrases. In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of a word to search for parts of words. At this time, we do not support full regular expressions nor exact phrase matches.

@@

\subsection{Scoring and Ranking}

do we want to do tf-idf? postgres document normalization?

>>>>

Queries to our full-text search engine can be words or phrases. In addition, they can contain a special wildcard symbol \textbf{\%} at the start or end of any word to search for parts of words. At this time, we do not support full regular expressions nor exact phrase matches.

@@

\subsection{Scoring and Ranking Results}

There are many ways to score and rank results of a search query. Some techniques, such as \textit{tf-idf}, require precalculated document metadata. Others require knowning positional information about a word within a document. We define several built-in ranking functions derived from PostgreSQL's built-in \texttt{ts\_rank} and \texttt{ts\_rank\_cd} functions that take in a \texttt{normalization} option, with integer inputs providing different types of document normalizations\footnote{http://www.postgresql.org/docs/8.3/static/textsearch-controls.html}.
The PostgreSQL's functions take into account how often the query terms appear in the document as well as how close together the terms are in the document. However, it is possible for a developer to implement their own ranking function and replace ours with theirs within Lucy.js.
